\documentclass[]{report}

\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=blue,
	urlcolor=black
}

% Title Page
\title{Sprint Reviews/Retrospectives}
\author{Engineering 72}


\begin{document}
	\maketitle
	
	\tableofcontents
	
	\chapter*{Sprint 0 - Planning}
	\addcontentsline{toc}{section}{Sprint 0 - Planning}
	\chapter*{Sprint 1}
		\addcontentsline{toc}{section}{Sprint 1}
		\section*{Review}
			\addcontentsline{toc}{subsection}{Review}
			For this sprint, the following user stories where scheduled to be completed:
			\begin{itemize}
				\item Refactoring/Fixing Logo Redirect.
				\item Refactoring/Fixing Login Page.
				\item Refactoring/Fixing Trainee management.
				\item Refactoring/Fixing Class Management.
				\item Setting attendance for all trainees.
				\item Being able to view all the trainees on the attendance page.
				\item Being able to view all the trainees on the assessment page.
				\item Reading the JSON from the API/JSON file into the database.
			\end{itemize}
			At the end of the Sprint, we were able to complete all the user stories except the following:
			\begin{itemize}
				\item Setting attendance for all trainees.
				\item Being able to view all the trainees on the assessment page.
				\item Reading the JSON from the API/JSON file into the database.
			\end{itemize}
			These tasks have been added with priority for the next sprint.
		\section*{Retrospective}
			\addcontentsline{toc}{subsection}{Retrospective}
			\subsection*{START}
				\begin{itemize}
					\item Grouping and helping people that are stuck
					\item Testing!!!
				\end{itemize}
				\subsection*{STOP}
				\begin{itemize}
					\item 
				\end{itemize}
				\subsection*{CONTINUE}
				\begin{itemize}
					\item Pair Programming - It was highly useful getting 
				\end{itemize}
	\chapter*{Sprint 2}
		\addcontentsline{toc}{section}{Sprint 2}
		\section*{Retrospective}
			\addcontentsline{toc}{subsection}{Retrospective}
			\subsection*{START}
				\begin{itemize}
					\item Working out Thymeleaf
					\item Asking for help if we need it.
				\end{itemize}
			\subsection*{CONTINUE}
				\begin{itemize}
					\item Working as a team
					\item Checking on everyone
					\item Testing
				\end{itemize}
			\subsection*{STOP}
				\begin{itemize}
					\item Working on our own when we are struggling
				\end{itemize}
\end{document}          